An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-21 neurips-19/poly-embed.tex
Reorg moving statements to Appendix

\jessie{Take out this paragraph?}
We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
Our results give a complete characterization in the case of dimension 1; that is, real-valued surrogates.
We find that a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
We show further that order-sensitivity characterizes the existence of \emph{any} real-valued convex surrogate, implying that embeddings lose no generality.
We conclude with preliminary results in higher dimensions and other future directions.

\subsection{Related works}
Convex surrogates have been formalized and investigated in a variety of past work such as \cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}, particularly in the context of 0-1 loss, distributions on just two outcomes, and support vector machines.
%  \cite{crammer2001algorithmic} is one of the first papers to present a convex surrogate for multiclass classification problems in the context of support vector machines.
%  They use the convex surrogate $L(\textbf{r},y) = (\max_{j\neq y} r_j - r_y + 1)_+$, where $\textbf{r}$ is a $n$-dimensional vector corresponding to the entire distribution, and $r_j$ is the $j^{th}$ component of \textbf{r}.
%
%  \cite{bartlett2006convexity} provides one of the most well-known formalizations of convex surrogates for properties on binary outcomes.
%  This work evaluates the risk bounds of convex surrogates and shows the sufficiency of convex surrogates such as logistic loss to replace the 0-1 loss for ease of optimization, and has inspired a line of research in the design of consistent surrogate losses for binary classification problems.
%  \jessiet{This is based on what I remember.  Couldn't find the free version (off the campus network) but also didn't look hard at all, since I'm guessing one of you two already knows this paper better than I do.}
%
%%  \cite{bartlett2008classification} studies the abstain property with $n=2$ and shows a variation of the hinge loss that is one convex surrogate that elicits the abstain property to two outcomes.
%
%  \cite{ramaswamy2012classification} discuss and formalize the notion of \emph{convex calibration} dimension for finite properties.
%  The concept they call convex calibration dimension is one notion of elicitation complexity discussion in this paper.
%  Denoted here by $\eliccvx(\gamma)$, convex calibration refers to the minimum dimension $d$ such that the property $\gamma$ can be indirectly elicited by a convex loss $L:\reals^d \to \reals^\Y_+$.
%
%  Most of the preliminary work on the construction of convex surrogate losses focuses on learning the mode in a binary classification problem.
  One of the first works formally studying convex surrogates beyond binary outcomes is~\cite{ramaswamy2018consistent}, who give an embedding of the \emph{abstain loss} into very few dimensions.
 For the case of $\reals^2$ \jessiet{$\reals^2$ or $n \in \{3, 4\}$?}, we will show that no embedding can do better. \jessiet{Take out this sentence?}

%  Rather than focusing on the mode, this paper proves bounds on the elicitation complexity of the abstain property.
%  They provide a consistent surrogate that elicits abstain with $\alpha = 1/2$ in $\ceil*{\log_2 n}$ dimensions. \jessiet{I don't like how much I'm talking about elicitation without the context.}
%  It remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that it is, at least from the perspective from ``embedding''.
%  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate for any dimension lower than $\ceil*{\log_2 n}$.
%
%  \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our \emph{surrogate property} that we elicit by a convex surrogate in lieu of directly eliciting a finite property.
%  However, they do not consider properties to be set-valued, leading to subtle differences in the property values for some distributions.
%  Additionally, most of their results focus on linear properties. \jessiet{is there a relationship between linear and orderable properties?  If not, we can probably remove this statement.}
%
  \cite{agarwal2015consistent} and~\cite{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
  These works are generally not directly comparable to our results, as they do not consider the embedding method. 
  Agarwal and Agarwal~\cite{agarwal2015consistent} also consider properties that are real-valued, rather than possibly set-valued as we do.
  However, we will mention relevant results inline.
%  In~\cite{ramaswamy2016convex}, the authors introduce a new method of obtaining upper bounds on elicitation complexity called the \emph{Feasible Subspace Dimension}.
%  This method uses local information about distributions in a property in order to find bounds on the convex elicitation complexity of a property.
%  For example, Feasible Subspace Dimension can be used to find a tight bound on $\eliccvx$(mode), but does not reveal a tight bound for the abstain property discussed later.
%  This suggests that the bound on $\eliccvx$(abstain) must be found using more \emph{global} information about the property.
%  We discuss this in Section~\ref{sec:general-dimensions}, showing previously unknown necessary conditions for embedding finite properties.

% \subsection{Notation}
% \begin{itemize}
%   \item $\Y$ is the finite outcome space, and $n := |\Y|$.
%   \item $\simplex\subseteq\reals^\Y$ is the set of distributions over $\Y$, thought of as vectors of probabilities.
%   \item For an outcome $y$, we denote $p_y$ as the probability of outcome $y$ being observed in nature.
%   \item If $\gamma = \prop{\ell}$, then $\gamma:\simplex \toto \R$ is the property elicited by the loss $\ell: \R \to \reals^\Y$.
%   \item $d$ is the dimension of the embedding space
%   \item $L:\reals^d \to \reals^\Y_+$ is a loss taking a report $u \in \reals^d$ and mapping the loss over each outcome in $\Y$. \raf{Changed to $\reals^\Y_+$ below.}
%   \item $\Gamma: \simplex \toto \reals^d$ is the set-valued property mapping a probability distribution to a report $u \in \reals^d$.
%   \item $\Gamma_u = \{ p \in \simplex : u \in \Gamma(p) \}$
%   \item $\psi$ is the link function (see below)
%   \item $\varphi:\R \to \reals^d$ is the embedding function
%   \item $\trim(\Gamma)$ and $\strip(\Gamma)$
%   \item $\eliccvx$, $\elicembed$, and $\elicpoly$
%   \item $V$ and $B(P)$ as we get ready for later.
% \end{itemize}

@@

\begin{definition}[Finite property, non-redundant]
  A property $\Gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ we have $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
  $\Gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
  We typically write finite properties in lower case, as $\gamma$.
\end{definition}

@@

\raf{Again, not sure we'll even need the property versions...}
With this terminology in hand, we can restate our definition of embedding.
First, we formalize the notion of embedding properties.
\begin{definition}
  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
\end{definition}
We can now see that a surrogate $L:\reals^d\to\reals^\Y$ embeds $\ell:\R\to\reals^\Y$ if and only if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.

@@

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
\end{proof}

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}

\end{proof}

@@

\begin{theorem}\label{thm:poly-embeds-discrete}
  Every polyhedral loss $L$ embeds a discrete loss.
\end{theorem}
\begin{proof}
  We merely show $L$ polyhedral $\implies$ $\risk{L}$ polyhedral, and apply Proposition~\ref{prop:embed-risk-poly}.
  \raf{Not sure how trivial this is, but it's definitely true.  I suspect it has a very short proof.}

  \jessie{Can also show that $L$ embeds $L|_\R$ like the original paper and use COLT Lemma 11/Lemma~\ref{lem:finite-full-dim}.}
\end{proof}

@@

\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
  Every discrete loss $\ell$ is embedded by a polyhedral loss.
\end{theorem}
\begin{proof}
  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
\end{proof}

@@

\begin{corollary}\label{cor:finite-elicit-embed}
  Let $\gamma$ be a finite property.
  The following are equivalent.
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\gamma$ is elicitable.
  \item $\gamma$ is embeddable.
  \item $\gamma$ is embeddable via a polyhedral loss.
  \end{enumerate}
\end{corollary}
\begin{proof}
  We trivially have $3\Rightarrow 2$.
  The direction $1\Rightarrow 3$ follows from Theorem~\ref{thm:discrete-loss-poly-embeddable}, by taking any discrete loss which elicits $\gamma$.
  Finally, to see $2\Rightarrow 1$,
  \raf{This follows from Proposition~\ref{prop:embed-trim}, but we're stating this as a corollary... let's see if it follows more directly from the above.  If it doesn't (one complication: there is no discrete loss starting from $2$ or $3$!) we can rephrase it as a theorem / proposition.}
\end{proof}

\hrule
\bigskip
OLD STUFF
\bigskip
\hrule

When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the loss.
As results in property elicitation typically assume non-redundant properties (e.g.~\cite{frongillo2014general,frongillo2015elicitation}) it is useful to consider a transformation which removes redundant level sets.
We capture this transformation as the trim operator presented below.

\begin{definition}\label{def:trim}
  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
\end{definition}
\raft{Note for later: should be able to show that the union of trim is the simplex.}

Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.

Before we state our first result, we will need to general lemmas about properties and their losses.
The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer} in the appendix), and its proof is omitted.
The second is closely related to the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).

We now state our first result, which shows remarkable structure of embeddable properties, and the properties that embed them.
First, we conclude that any embeddable property must be elicitable.
We also conclude that if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
(When working with convex losses, these extra reports are typically the convex hull of the embedded reports.)
In this sense, we can regard embedding as a minor departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trim(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.
\raft{Commented out what used to be before trim; not 100\% sure how to integrate.}
% Looking at the $\trim$ of a property allows us to relate the finite property of interest to the subtlely different surrogate property that we actually elicit when embedding the original property into $\reals^d$.
% In the surrogate property, there is often an infinite set of ``hidden'' level sets corresponding to the reports in the convex hull of embedded points whose level sets have nonempty intersection.
% Taking the $\trim$ thus allows us to remove labels so that we can relate the optimal sets of original reports and their embedded points, and then we remove the ``hidden'' level sets that are only optimal when we are indifferent between a subset of the embedded points.

\begin{proposition}\label{prop:embed-trim}
  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
  The following are equivalent:
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
  \item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
  \end{enumerate}
  Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
\end{proposition}

To be useful in applications, a loss which embeds a property must be accompanied by a calibrated link to that property.
The definition of embedding makes part of the link clear: the link should map embedded reports back to the original reports, since they are equivalent in a strong sense.
It is not a priori clear how to map the remaining reports, however.
Fortunately, using the machinery developed in Proposition~\ref{prop:embed-trim}, we can easily construct a calibrated link on the remaining reports.

\begin{proposition}\label{prop:embed-link}
  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
  Then there is a calibrated link from $\Gamma$ to $\gamma$. % which can be taken to be separated if $L$ is polyhedral.
\end{proposition}
\begin{proof}
  Let $\gamma:\simplex\toto\R$.
  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
  The link $\psi : \reals^d \to \R$ which encodes these choices is calibrated.
  \raft{Commented out the separated stuff}
  % Now assume $L$ is polyhedral.
  % \jessiet{Hole jere: $j$-faces of the function.}
  % For the second part of the statement, in order for $\psi$ to be separated, for $\epsilon > 0$, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
  % If the loss $L$ is polyhedral, we want to show that we can construct a $\psi$ so that the above holds.
  %
  % First, consider that each of the embedded points in $u \in \varphi(\R)$ must have ball $B(\epsilon, u)$ centered on $u$ so that no other $w \in \varphi(\R)$ is in $B(\epsilon, u)$.
  % If this is not true, then \jessie{...?} \jessiet{I'm not sure how this messes with things, but I would think the level sets corresponding to the two points would differ on a set of zero measure, if at all, or both be in the $\arginf$of the loss...?}
  %
  % Now for any $u \in \varphi(\R)$ and $v \in B(\epsilon, u)$, if $\psi(v)$ does not map to $\psi(u)$, then there must be some other $w \in \varphi(\R)$ so that $\psi(v) = \psi(w)$.
  % Since $L$ is polyhedral, we know that for $p \in \simplex$ such that $v \in \Gamma(p)$, then since $u$ and $v$ are sufficiently close, $\E_p L(w,Y) = \E_p L(v,Y) \leq \E_p L(u,Y)$.
  % However, if the inequality was strict, then we contradict the polyhedral structure of $L$, since $v$ is not an embedded point.
  % Therefore, $v \in \Gamma(p) \implies u \in \Gamma(p)$, and we can alter the link function so that $\psi(v) = \psi(u)$.
  %
  %
  % If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
%Additionally, if $\psi$ was not selective, then we know $\psi(v) = \psi(w)$ for some embedded point $w \neq u$.
%Since the losses of $u$ and $v$ are not bounded about away from each other and $\psi(v) = \psi(w)$, then the loss $L$ must be constant on $\conv(\{u,v,w\})$, otherwise we would either contradict elicitability of $\Gamma$ or the construction of the calibrated link $\psi$.
%Therefore, we can reassign $\psi(v) = \psi(u)$ for any $v\in B(\epsilon, u)$, and such a link additionally separated.
\end{proof}
In typical applications, one requires more of the link, namely that it should be separated (see Definition~\ref{def:links}).
In most cases, devising a separated link is straightforward, for example with polyhedral losses using bullet 3 in Theorem~\ref{thm:finite-elicit-embed} below.
Giving a construction that yields a separated link for all polyhedral losses is a challenging open question.
\raft{Replace this paragraph with gloating about our result if we actually give this construction.}

@@

\begin{proposition}
  If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistenty with $\ell$.
\end{proposition}
\begin{proof}
  \raf{Use Hari's theorems from their section 8.}
\end{proof}

@@

Rather than formally define the Lov\'asz hinge, we defer the full analysis to the original version of the paper~\cite{yu2015lovaszarxiv}\raf{CITE -- arXiv} \jessie{Apparently the fullversion is the bad one, so maybe we say original?}, and focus here on the $k=2$ case.
For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
Assuming $g$ is normalized and increasing (meaning $g_{1,2} \geq \{g_1,g_2\} \geq g_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
\begin{multline}
  \label{eq:lovasz-hinge}
  L^g(u)_y = \max\Bigl\{(1-u_1y_1)_+ g_1 + (1-u_2y_2)_+ (g_{1,2}-g_1),\\[-4pt] (1-u_2y_2)_+ g_2 + (1-u_1y_1)_+ (g_{1,2}-g_2)\Bigr\}~,
\end{multline}
where $(x)_+ = \max\{x,0\}$.
We will explore the range of values of $g$ for which $L^g$ is consistent, where the link function $\psi:\reals^2\to\{-1,1\}^2$ is fixed as $\psi(u)_i = \sgn(u_i)$, with ties broken arbitrarily.

>>>>

%\jessie{Take out this paragraph?}
%We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
%Our results give a complete characterization in the case of dimension 1; that is, real-valued surrogates.
%We find that a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
%We show further that order-sensitivity characterizes the existence of \emph{any} real-valued convex surrogate, implying that embeddings lose no generality.
%We conclude with preliminary results in higher dimensions and other future directions.

\subsection{Related works}
Convex surrogates have been formalized and investigated in a variety of past work such as \cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}, particularly in the context of 0-1 loss, distributions on just two outcomes, and support vector machines.

  One of the first works formally studying convex surrogates beyond binary outcomes is~\cite{ramaswamy2018consistent}, who give an embedding of the \emph{abstain loss} into very few dimensions.
 For the case of $\reals^2$ \jessiet{$\reals^2$ or $n \in \{3, 4\}$?}, we will show that no embedding can do better. \jessiet{Take out this sentence?}

  \cite{agarwal2015consistent} and~\cite{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
  These works are generally not directly comparable to our results, as they do not consider the embedding method. 
  Agarwal and Agarwal~\cite{agarwal2015consistent} also consider properties that are real-valued, rather than possibly set-valued as we do.
  However, we will mention relevant results inline.

@@

@@

\raf{informal descriptions of the hinge property and illustrate how it simplifies the embedding condition; cite appendix for the formal def of embedding property}

\begin{theorem}\label{thm:polyhedral-embed-prop}
	Every polyhedral loss embeds a finite elicitable property.
	%Moreover, a polyhedral loss $L$ indirectly elicits a non-redundant elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
\end{theorem}

@@

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  \raft{Forward: you had the right idea that this is mainly Lemma 11.  But you have to step through the logic much more carefully, and be rigorous.  Keep in mind: you already have $\varphi$ from the embedding, and you know the loss values match.  It's true that you need to map $u$ values to $r$ values, but what you have doesn't make sense.}    
  For the forward implication, suppose $L$ embeds the discrete loss $\ell$ via the embedding $\varphi$.
  Then $\Gamma := \prop{L}$ embeds the finite property $\gamma:\simplex \toto \R$ elicited by $\ell$.
  Call $\U := \varphi(\R)$.
%  $\gamma'(p) := \Gamma(p) \cap \U$ is nonempty for all $p \in \simplex$ because $r \in \gamma(p) \implies \varphi(r) \in \Gamma(p)$ for all $p \in \simplex$, and by definition $\varphi(r) \in \U$, so $\varphi(r) \in \gamma'(p)$ for all $p \in \simplex$.
  $\gamma'(p) := \Gamma(p) \cap \U$ is nonempty for all $p \in \simplex$ as $r \in \gamma(p) \implies \varphi(r) \in \gamma'(p)$ by the definition of embedding and nondegeneracy of $\gamma$.
  By Lemma~\ref{lem:loss-restrict}, we know that $L|_{\U}$ elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.

%  As $|\R| = |\R'|$, we know there is a bijection from one to the other defined by the embedding $\varphi$ on a restricted domain.
  By embedding, the loss values $L(\varphi(r)) = \ell(r)$ for all $r \in \R$, and so the expected values $\inprod{p}{L(\varphi(r))} = \inprod{p}{\ell(r)}$ for all $p \in \simplex$ and $r \in \R$.
  In particular, $\min_{u \in \R'}\inprod{p}{L(u)} = \min_{r \in \R}\inprod{p}{\ell(r)}$ for all $p \in \simplex$. 
  Therefore, we can conclude that $\risk{L|_{\R'}} = \risk{\ell}$.
  Combining with the above statement, we conclude $\risk{L} = \risk{\ell}$.

  \raft{Reverse: The high-level idea is that the projections (power diagrams) of $\risk{\ell}$ and $\risk{L}$ are the same, so since $\prop{\ell}$ has finitely many full-dimensional level sets, so does $\prop{L}$.  The property part of the embedding then follows; just take any $u_f$ like you have.  It remains to show that the losses themselves must match up; this is what the FK result is useful for.  Note though that you can't conclude that the minimizers are unique (and it's not true) since $\prop{L}$ is not redundant, as assumed in that paper.
    All that said, I'm pretty confused by what you are trying to do; seems like your contradiction is going the wrong way, and several steps are missing justification.}

  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
  Since $\ell$ is discrete, we know these risks are polyhedral, as $\risk{\ell}$ is the pointwise min of a finite set of linear functions.
  The projection of their epigraphs onto $\simplex$ forms a power diagram by \ref{thm:aurenhammer}, and since the risks are the same, we know the corresponding power diagrams are equal.  %, corresponding to the level sets of the properties each loss elicits.
  Observe there are only finitely many cells in a power diagram; we call the set of full-dimensional cells in the power diagram $F$.
  We claim that each cell $f \in F$ is then a level set $\gamma_r$ for some $r \in \R$, and equivalently, $\Gamma_{u_f}$ for some $u_f \in \reals^d$.
  We go on to embed $\varphi: r \mapsto u_f$ for each $r \in \R$.
  (By regularity assumptions, we consider that there is an $f \in F$ corresponding to each $r \in \R$.)

  Now, for each $f \in F$, fix some distribution $p \in \inter{f}$.
  The supporting hyperplane of $\risk{\ell}(p)$ is unique, since $p$ belongs to exactly one facet of $\risk{\ell}$ (i.e. $\risk{\ell}(p)$ is differentiable.)
  Since $\ell$ is discrete, the coefficients of the supporting hyperplane (in $\simplex \subseteq \reals^n$) exactly describe the loss over each outcome given the report $r \in \gamma(p)$.  \jessie{Double check??}

  Now choose some $u_f \in \argmin_{u'} L(u', p)$; we design $\varphi : r \mapsto u_f \in \Gamma(p)$.
  Since $\risk{L}$ is polyhedral, the supporting hyperplane to $\risk{L}$ is unique for each $p \in \inter{f}$ and $f \in F$, and so the loss $L(u_f)$ is equal to $\risk{L}(p)$ for all such $p$.
  \jessie{Don't think I phrased this correctly. revisit.}
  Therefore, $u_f \in \Gamma(p)$ for all $p \in f$ since level sets of a property are closed.

  We claim that $L$ embeds $\ell$, since we have $r \in \argmin_{r' \in \R} \ell(r', p) \iff \varphi(r) \in \argmin_{u' \in \U} L(u', p)$ by our design of $\varphi$.
  Moreover, the equlity of $\ell(r)$ and $L(\varphi(r))$ can be seen by the risks being the same, and therefore so are the supporting hyperplanes (defining the loss values at $\ell(r)$ and $L(\varphi(r))$) for all $p \in f$ and $f \in F$, since $\cup_F f = \simplex$.  
\end{proof}

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral as $\risk{\ell}$ is the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
  Therefore, $\risk{L}$ is polyhedral.

  The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
  Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
  Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
  For each $f \in F$, there is a distribution $p \in \inter{f}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
  Pick some $u_f \in \argmin_{u' \in \U}L(u', p)$.
  The coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u_f)$.
  Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
  Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
\end{proof}

@@

\begin{theorem}\label{thm:poly-embeds-discrete}
  Every polyhedral loss $L$ embeds a discrete loss.
\end{theorem}
\begin{proof}
  The result is a Corollary of Theorem~\ref{thm:polyhedral-embed-prop} \jessie{and statement on matching losses.}.
\end{proof}

@@

\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
  Every discrete loss $\ell$ is embedded by a polyhedral loss.
\end{theorem}
\begin{proof}
  \raf{NOTE: need to ensure nonnegativity of $L$}
  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
\end{proof}

@@

%\begin{corollary}\label{cor:finite-elicit-embed}
%  Let $\gamma$ be a finite property.
%  The following are equivalent.
%  \begin{enumerate}\setlength{\itemsep}{0pt}
%  \item $\gamma$ is elicitable.
%  \item $\gamma$ is embeddable.
%  \item $\gamma$ is embeddable via a polyhedral loss.
%  \end{enumerate}
%\end{corollary}
%\begin{proof}
%  We trivially have $3\Rightarrow 2$.
%  The direction $1\Rightarrow 3$ follows from Theorem~\ref{thm:discrete-loss-poly-embeddable}, by taking any discrete loss which elicits $\gamma$.
%  Finally, to see $2\Rightarrow 1$,
%  \raf{This follows from Proposition~\ref{prop:embed-trim}, but we're stating this as a corollary... let's see if it follows more directly from the above.  If it doesn't (one complication: there is no discrete loss starting from $2$ or $3$!) we can rephrase it as a theorem / proposition.}
%\end{proof}

\jessie{Do we want this at all?}
To be useful in applications, a loss which embeds a property must be accompanied by a calibrated \jessie{separated?}link to that property.
The definition of embedding makes part of the link clear: the link should map embedded reports back to the original reports, since they are equivalent in a strong sense.
It is not a priori clear how to map the remaining reports, however.
Fortunately, using the machinery developed in Proposition~\ref{prop:embed-trim}, we can easily construct a calibrated link on the remaining reports.

\begin{proposition}\label{prop:embed-link}
  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
  Then there is a calibrated link from $\Gamma$ to $\gamma$. % which can be taken to be separated if $L$ is polyhedral.
\end{proposition}
\begin{proof}
  Let $\gamma:\simplex\toto\R$.
  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
  The link $\psi : \reals^d \to \R$ which encodes these choices is calibrated.
  \raft{Commented out the separated stuff}
  % Now assume $L$ is polyhedral.
  % \jessiet{Hole jere: $j$-faces of the function.}
  % For the second part of the statement, in order for $\psi$ to be separated, for $\epsilon > 0$, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
  % If the loss $L$ is polyhedral, we want to show that we can construct a $\psi$ so that the above holds.
  %
  % First, consider that each of the embedded points in $u \in \varphi(\R)$ must have ball $B(\epsilon, u)$ centered on $u$ so that no other $w \in \varphi(\R)$ is in $B(\epsilon, u)$.
  % If this is not true, then \jessie{...?} \jessiet{I'm not sure how this messes with things, but I would think the level sets corresponding to the two points would differ on a set of zero measure, if at all, or both be in the $\arginf$of the loss...?}
  %
  % Now for any $u \in \varphi(\R)$ and $v \in B(\epsilon, u)$, if $\psi(v)$ does not map to $\psi(u)$, then there must be some other $w \in \varphi(\R)$ so that $\psi(v) = \psi(w)$.
  % Since $L$ is polyhedral, we know that for $p \in \simplex$ such that $v \in \Gamma(p)$, then since $u$ and $v$ are sufficiently close, $\E_p L(w,Y) = \E_p L(v,Y) \leq \E_p L(u,Y)$.
  % However, if the inequality was strict, then we contradict the polyhedral structure of $L$, since $v$ is not an embedded point.
  % Therefore, $v \in \Gamma(p) \implies u \in \Gamma(p)$, and we can alter the link function so that $\psi(v) = \psi(u)$.
  %
  %
  % If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
%Additionally, if $\psi$ was not selective, then we know $\psi(v) = \psi(w)$ for some embedded point $w \neq u$.
%Since the losses of $u$ and $v$ are not bounded about away from each other and $\psi(v) = \psi(w)$, then the loss $L$ must be constant on $\conv(\{u,v,w\})$, otherwise we would either contradict elicitability of $\Gamma$ or the construction of the calibrated link $\psi$.
%Therefore, we can reassign $\psi(v) = \psi(u)$ for any $v\in B(\epsilon, u)$, and such a link additionally separated.
\end{proof}

In typical applications, one requires more of the link, namely that it should be separated (see Definition~\ref{def:links}).
In most cases, devising a separated link is straightforward.
Giving a construction that yields a separated link for all polyhedral losses is a nuanced problem described in the following section.
\raf{Replace this paragraph with gloating about our result if we actually give this construction.}

@@

\begin{lemma}
  \label{lem:polyhedral-range-gamma}
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma := \prop{L}$.
  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
\end{lemma}

\begin{proposition}
  If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistenty with $\ell$. \jessie{Rephrase?}
\end{proposition}
\begin{proof}
  \raf{Use Hari's theorems from their section 8.}
\end{proof}

@@

Rather than formally define the Lov\'asz hinge, we defer the full analysis to the original version of the paper~\cite{yu2015lovaszarxiv}, and focus here on the $k=2$ case.
For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
Assuming $g$ is normalized and increasing (meaning $g_{1,2} \geq \{g_1,g_2\} \geq g_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
\begin{multline}
  \label{eq:lovasz-hinge}
  L^g(u)_y = \max\Bigl\{(1-u_1y_1)_+ g_1 + (1-u_2y_2)_+ (g_{1,2}-g_1),\\[-4pt] (1-u_2y_2)_+ g_2 + (1-u_1y_1)_+ (g_{1,2}-g_2)\Bigr\}~,
\end{multline}
where $(x)_+ = \max\{x,0\}$.
We will explore the range of values of $g$ for which $L^g$ is consistent, where the link function $\psi:\reals^2\to\{-1,1\}^2$ is fixed as $\psi(u)_i = \sgn(u_i)$, with ties broken arbitrarily.
